A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-01-09 for_submission/rvaught_2018.tex
9/15

\section{Introduction}\label{sec:intro}
Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain. Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}). Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.

An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (e.g., \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
While this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.

An alternative method that can in principle assess the radial extent and morphology of outflows is to trace the gas in emission. This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock-heated phase of the gas. 
Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
\citep[UV;][]{{Weiner2009, Kornei2013}}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$. In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).

Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and the VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013}, \citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.

The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds. \citet{Prochaska_2011} have used this technique to predict 
spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ fine-structure transitions for a variety of wind morphologies. The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission lines with similar equivalent widths (EW). Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission by a factor proportional to the angular extent (i.e., solid angle) of the wind. Scattered emission was found to be additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM). Thus, spatially-resolved measurement of the surface brightness of this emission constrains not only the radial extent of the emitting material, but also its morphology and dust content.

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to 1D spectra, the narrowband imaging constrains the surface brightness and radial extent of the wind. These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made using radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

@@

\subsection{VLT/FORS2 Observations}
Our narrow-band imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\textbf{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck/LRIS program.  A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).  The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.

@@

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{$\log$(SFR)} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($\log M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. These values differ slightly from those reported by the European Southern Observatory. \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(S)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{FWHM of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\ 
\\

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival European Southern Observatory (ESO) calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. 
We perform absolute flux calibration using the methods of \cite{Jacoby1987}. We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the latest CALSPEC spectral library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the above assumption . 
The conversion from count rate to flux units for each filter is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{Top: Stacked HeII+47 image of the galaxy sample. Bottom: Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows half of the total FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To achieve both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission. For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest frame. %The galaxy excluded from our analysis is J.57. 
The spectral coverage of these filters is qualitatively different for the fifth galaxy in our sample (J.57).
As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are equally sampled by both of our filters. When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting both \ion{Mg}{2} emission (if present) and the continuum. We thus use this galaxy as check on the quality of our continuum subtraction.

@@

Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

@@

Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$. The observed-frame EW$_{\rm{MgII}}$ images are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).

>>>>

\section{Introduction}\label{sec:intro}
Galactic winds likely play a critical role in regulating the star formation rates and stellar masses of galaxies (e.g., \citethnop{SP1999}; \citethnop{Keres2009}; \citethnop{Oppenheimer2010}; \citethnop{Hopkins2014}; \citethnop{Werk_2014}); however, the physics that powers these winds remains uncertain. Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{MO1977}; \citethnop{Chevalier_1985}; \citethnop{Breitschwerdt1991}; \citethnop{Springel_2003}; \citethnop{Murray2011}; \citethnop{Uhlig2012}).
%\citethnop{Sugahara_2017}
Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.

An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxy spectroscopy 
(e.g., \citethnop{Heckman2000}; \citethnop{Shapley2003}; \citethnop{Rupke2005b}; \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g., \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
However, while this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.

An alternative method that can in principle assess the radial extent and morphology of outflows is to trace the gas in emission. This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Heckman1990,Lehnert1999,Veilleux2003,Matsubayashi2009}} %Veilleux2009}
% I removed Veilleux2009 as it is about imaging in the near-IR tracing molecular gas 
as these transitions are sensitive to the warm shock-heated phase of the gas. 
Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
\citep[UV; e.g.,][]{{Weiner2009, Kornei2013}}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the Keck/Low Resolution Imaging Spectrometer (LRIS) spectrum of a strongly star-forming galaxy at redshift $z = 0.694$. In addition, the emission was spatially extended beyond the galaxy continuum, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption is observed to be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely toward the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (e.g., \citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).

Since the first detection of \ion{Mg}{2} emission in 
an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in galaxy surveys conducted with Keck/LRIS, the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS), the VLT Multi Unit Spectroscopic Explorer (MUSE), and the MMT Blue Channel Spectrograph  (\citethnop{Weiner2009}; \citethnop{Erb2012}; \citethnop{Kornei2013}; \citethnop{Feltre2018}; \citethnop{Henry2018}). These surveys, which include galaxies with redshifts $ 0.20 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles, and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.

The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds. \citet{Prochaska_2011} have used this technique to predict 
spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ fine-structure transitions for a variety of wind morphologies. The authors demonstrated that isotropic, dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission lines with similar equivalent widths (EW). Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission by a factor proportional to the angular extent (i.e., solid angle) of the wind. Scattered emission was found to be additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM). Thus, spatially-resolved measurement of the surface brightness of this emission constrains not only the radial extent of the emitting material, but also its morphology and dust content.

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter'' covering the \ion{Mg}{2} doublet in the observed frame, and a ``continuum filter'' that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to slit or fiber spectra, the narrowband imaging fully constrains the surface brightness and projected radial extent of the wind. These observations allow us to create the first ever high-S/N spatially-resolved map of both detection limits on \ion{Mg}{2} emission and on \ion{Mg}{2} absorption.

In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made using radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

@@

\subsection{VLT/FORS2 Observations}
Our narrowband imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{\emph{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\emph{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

\subsection{Supplemental Keck/LRIS Spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck/LRIS program.  A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).  The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.

@@

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{$\log$(SFR)} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($\log M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. 
%These values differ slightly from those reported by the European Southern Observatory.
 \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{FWHM of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\ 
%\\

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival European Southern Observatory (ESO) calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. 
We perform absolute flux calibration using the methods of \cite{Jacoby1987}. We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
However, since our filter transmission curves are sampled at wavelength intervals similar to the sampling of the spectrum of GD50 from the latest CALSPEC spectral library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the above assumption. 
The conversion from count rate to flux units for each filter is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{\emph{Top:} Stacked HeII+47 image of the galaxy sample. \emph{Bottom:} Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows approximately half of the total FORS2 FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To achieve both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission. For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest frame. %The galaxy excluded from our analysis is J.57. 
The spectral coverage of these filters is qualitatively different for the fifth galaxy in our sample (J.57).
As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are approximately equally sampled by both of our filters. When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting both \ion{Mg}{2} emission (if present) and the continuum. We thus use this galaxy as check on the quality of our continuum subtraction.

@@

Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.  We thus do not apply any spectral correction in the following analysis.

@@

Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$. %The observed-frame EW$_{\rm{MgII}}$ images 
They are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
